\Large \bf The Effects of Weather on Maize Yields: New Evidence from Kenya

### 2018-11-28 writing/draft2/draftMonika14.tex
draft

 \item[] \textbf{Paragraph 2}
\begin{itemize}
\item Data
\begin{itemize}
\item \textit{Just write where the data come from, not much detail needed}
\end{itemize}
\end{itemize}

@@

\subsection{Data}
\begin{itemize}
\item \textcolor{blue}{Source of data}
\item \textcolor{blue} {Verbal description of the data, resolution, period, frequency}
\item \textcolor{blue} {Plot(s)/barplots of yield, precip. and temp.}
\item \textcolor{blue}{Maybe a table of descriptive statistics or ref. to a table in the Appendix}
\item \textcolor{blue}{Description how the weather data were aggregated spatially over counties}
\end{itemize}

>>>>

\subsection{Data}\label{Data}
\begin{itemize}
\item Source of the climate data (Boku and Berkeley)
\item Source of the yield data (Kenya MoA)
\end{itemize}

@@
